Augmentation of a Model Historical Harpsichord Mechanism for Haptic Enabled Interaction

### 2025-01-17 src/main.tex
abstract

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{nimeart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Presented is a design for an electronically augmented replica of a 16th century
harpsichord interface, in the style of a 1547 Trasuntino harpsichord. The
interface was designed, fabricated, and exhibited in a collaboration between the
NEMUS project at the Università di Bologna and the Museo San Colombano, which
hosts the Tagliavini Collection of playable historical keyboard instruments. The
interface was commissioned as part of an exhibition and as a means of
interacting with items in the collection that are no longer in playing
condition. The keyboard is a replica of the mechanism found in harpsichords in
the Trasuntino style, with un-pitched strings under tension to provide a
comparable mechanical resistance as found on an original. A system of infra-red
LED / phototransistor pairs was connected to a microcontroller and installed
inside the interface from which a stream of data can be generated for each jack.
The paper covers the design criteria, process, open source development, and
execution of installation for exhibition at San Colombano.
\end{abstract}

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
A project of this breadth developed across 3 institutes and 2 countries
cannot be carried without the support and technical knowledge of many
skilled and passionate people.

We acknowledge the invaluable contributions of

@@

    \begin{itemize}
    \tightlist
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}
\end{acks}

>>>>

%%
%% This is file `sample-nime-paper.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-nime-paper.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% History of NIME Template Updaters:
%% Modified by Florent Berthaut, Charles Martin, Yichen Wang, 21 November 2024
%% Modified by Adnan Marquez-Borbon 30 November 2022
%% Modified by Courtney Reed 28 November 2022
%% Modified by Joe Wright 14 December 2019
%% Modified by Niccolò Granieri 10 October 2018
%% Modified by Angelo Fraietta 23 December 2018
%% Modified by Angelo Fraietta 22 November 2018
%% Modified by Rodrigo Schramm on 22 September 2018
%% Modified by Luke Dahl on 17 October 2-17
%% Modified by Cumhur Erkut on <2016-10-11 Tue>
%% Modified by Edgar Berdahl on 5 November 2014
%% Modified by Baptiste Caramiaux on 25 November 2013
%% Modified by Kyogu Lee on 7 October 2012
%% Modified by Georg Essl on 7 November 2011
%%
%% And here's the template:
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{nimeart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{nimeart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf,anonymous]{nimeart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
This work describes the design of an electronically augmented replica of a 16th-century harpsichord keyboard with a typical Renaissance Italian layout. The keyboard is a collaboration between the authors and the Museo di San Colombano, which houses the Tagliavini Collection of playable historical keyboard instruments. The keyboard was commissioned for exhibition purposes and to enhance the experiential authenticity of the collection. The keyboard emulates the mechanics of a two-register harpsichord featuring a single manual. Unpitched strings under tension replicate the mechanical resistance characteristic of the original compass. An array of infrared LED/phototransistor pairs, connected to a microcontroller, was installed within the interface to generate a continuous stream of data corresponding to the jacks' motion. This paper details the design principles, development process, open-source implementation, and realisation of the installation for the San Colombano exhibition.
\end{abstract}

@@

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.

\section{Ethical Standards}\label{ethical-standards}

% \begin{anonsuppress}

This work was performed at \anon{San Colombano}
To ensure objectivity and transparency in research and to ensure that
accepted principles of ethical and professional conduct have been
followed, authors must include a section ``Ethical Standards'' before
the References. This section should include (if relevant): information
regarding sources of funding, potential conflicts of interest (financial
or non-financial), informed consent if the research involved human
participants, statement on welfare of animals if the research involved
animals or any other information or context that helps ethically situate
your research. For help with the ethics section, feel free to ask on the
NIME forum: \url{https://forum.nime.org}.
% \end{anonsuppress}

\begin{acks}

% \begin{anonsuppress}
% This is the continuation of the previous work by the author
% A project of this breadth developed across 3 institutes and 2 countries
% cannot be carried without the support and technical knowledge of many
% skilled and passionate people.
% \end{anonsuppress}

% \begin{anonsuppress}
% A project of this breadth developed across 3 institutes and 2 countries
% cannot be carried without the support and technical knowledge of many
% skilled and passionate people.
% \end{anonsuppress}

\begin{anonsuppress}
We acknowledge the invaluable contributions of

@@

    \begin{itemize}
    \tightlist
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}

\end{anonsuppress}
\end{acks}
